---
title: "Report on Survey among Students of Cognitive Science / Computing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, echo = F)
```

```{r, echo = F}

library(tidyverse)
library(scales)
library(reticulate)

```

```{python}
# standard imports 
import numpy as np
import pandas as pd 
import matplotlib.pyplot as plt
import seaborn as sns
# sns.set_style("whitegrid")

# download the answer file from "Google Sheets" as a csv and save on your computer
filepath = 'data-raw.csv' # change to your specific filepath (be aware of Windows/Linux/Apple conventions)

# Mood & Impressions
part1_1 = pd.read_csv(filepath, header=0, usecols = [1,2,3], names = ["Studies", "GeneralMood", "Expectations"]) #closed questions
part1_2 = pd.read_csv(filepath, header=0, usecols = [4]) # open questions

# Visualization of the first block of questions (closed ones)
mean1_1 = part1_1[["Studies", "GeneralMood", "Expectations"]].mean()
print("How is the the first online semester holding up in regards to your...\n",mean1_1.round(decimals =2))

# To plot general mood and impressions 
fig1_1, ax1_1 = plt.subplots()
ax1_1.set_title('How is the the first online semester holding up in regards to your...')
part1_1[["Studies", "GeneralMood", "Expectations"]].boxplot(ax = ax1_1)
plt.xticks(ticks= [1,2,3],labels = ["Studies","General\nMood", "Expectations"],fontsize = "large")
plt.ylabel("Bad                                                     Well")

plt.show()
```



# Section 5 Social Life/Collaboration


Reading in and isolating the specific part
```{r}
#filepath = "/home/god/Desktop/XY/uni/SS20/SOS/CogSciSOS.csv"
social = read_csv(filepath) %>% select(35:37)
```



Plots of the three questions
```{r}
ggplot(social)  + geom_bar(aes( stringr::str_wrap(`How often do you arrange meetings with other people for studying?`, 20))) + xlab("How often do you arrange meetings with other people for studying?")


ggplot(social)  + geom_bar(aes( stringr::str_wrap(`Do you meet virtually with people for studying?`, 20))) + xlab("Do you meet virtually with people for studying?")

ggplot(social)  + geom_bar(aes( stringr::str_wrap(`Would you wish there would be offer more online social events?`, 20))) + xlab("Would you wish there would be offer more online social events?")
```


```{r}
# read in the data
d <- read_csv('data-raw.csv')
# get the relevant part
d_problems <- d %>% select(`How problematic was the summer term 2020 for you in general?`:`To cope with any arising issues, which of the following services have you used?`)
# use more tractable col names 
colnames(d_problems) <- c(
  "how problematic",
  "which problems",
  "psychol. problem?",
  "psychol. problem worsened?",
  "personal report",
  "services used"
)
```

# Questions about problems

INSERT TEXT: Motivation behind this question set (copy-paste in part from survey).

## Q4.1: "How problematic was the summer term 2020 for you in general?"

The question asked was "How problematic was the summer term 2020 for you in general?". Answers could be given on a 10-point Likert scale ranging from 1 (= very easy / no problems at all) to 10  (= very problematic / many problems). The distribution of answers is shown below. 

```{r}
d_problems %>% 
  # mutate(`how problematic` = as.character(`how problematic`)) +
  ggplot(aes(x = `how problematic`)) +
  geom_bar() +
  scale_x_discrete(limits = 1:10) +
  labs(
    x = "rating",
    y = "frequency",
    title = "How problematic was the SS 2020 in general (1 = easy; 10 = hard)?"
  )
```




