---
title: "Report on Survey among Students of Cognitive Science / Computing"
author: "Michael Franke, Kristina Kobrock, Laura Krieger, Sarah Neuhoff, Alessandro Schlott, Leon Schmid, Lea Tiyavorabun and Benjamin Werk"
output:
  html_document:
    toc: true
    toc_depth: 2
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, echo = F, cache = F)
```

```{r, echo = F}
library(tidyverse)
library(scales)
library(reticulate)
```

The students of Cognitive Science (BSc, MSc) and Cognitive Computing (MSc) were invited to take part in a voluntary online survey to be completed between June 11th and June 16th of 2020. The survey was hosted on Google Forms. All data was handled anonymously. The survey can be inspected [here](https://forms.gle/vf6w6rCUeAxPXbjM9). Participation in the survey was elicited by an email to "studall" which also contained information on where to find help with various problems.

The goal of this initiative was to obtain feedback from our students on:

- how they experienced the "digital" summer term 2020 so far
- in particular, which problems and obstacles were encountered
- how, based on these experiences, digital teaching can be improved in the future

In the following we descriptively reproduce the results from all the questions asked with little interpretation or redaction. Only few comments to open-ended questions were removed in case they targeted specific courses or persons.

Cheers to everyone who participated in this survey and many thanks also to the volunteers who helped in the creation of the survey and the data analysis. In alphabetical order the contributors were: Michael Franke, Kristina Kobrock, Laura Krieger, Sarah Neuhoff, Alessandro Schlott, Leon Schmid, Lea Tiyavorabun and Benjamin Werk.


# 1. Mood and Impression

The first part of the survey asked for general mood and impressions. It asked the questions:

> Compared to the last one, how does your first digital semester work for you so far regarding your ...
>
> - ... **studies**?;
>
> - ... general **mood**?;
>
> - ... **expectations** (worse/better than expected)?

Answers could be given on a 10-point Likert scale ranging from 1 (= sad smiley) to 10  (= happy smiley). The distribution of answers is shown below.


```{r}
general <- read_csv('rand.csv') %>% select(2:6) %>% 
  mutate(
    studies = `... regarding your studies:`,
    mood = `... regarding your general mood:`,
    expectations = `... regarding your expectations (worse/better than expected?):`
  )
```


```{r}

general %>%
  select(studies, mood, expectations) %>% 
  pivot_longer(cols = everything(), names_to = "question", values_to = "answer") %>% 
  mutate(question = factor(question, levels = c("studies", "mood", "expectations"))) %>% 
  ggplot(aes( x = answer)) +
  geom_bar() +
  scale_x_discrete(limits = 1:10) +
  facet_grid(question~.) +
  labs(
    x ="rating",
    y = "frequency",
    title = "How are your studies going during the digital semester?  (1 = bad , 10 = great)"
  )

```

We also provided room for open feedback:

> If you want to name reasons for the above, please drop a line.
    
Here is what was submitted:


```{r, results = 'asis'}
q14 <- general %>% select(4)
q14 <- general %>% select(`If you want to name reasons for the above, please drop a line.`) %>%
  filter(! is.na(`If you want to name reasons for the above, please drop a line.`)) %>%
  pull(`If you want to name reasons for the above, please drop a line.`) %>%
  as.character()
cat(paste('1.', q14 ), sep = '\n')
```


# 2. What works well online? What doesn't?

In this section we were are asking for the students experience with the online semester, in particular with different formats of teaching, learning etc.

## Rating scale answers

First participants were asked to indicate how much they agree with the following statements with the ongoing semester in mind on a 10-point Likert scale ranging from 1 (= I do not agree) to 10 (= I agree):

> The online format works well for ...
> 
> - **lectures** (lecturer presents information)
> 
> - **tutorials** (teacher presents and discusses exercises and solutions)
> 
> - **"Testate"** (students present homework to e.g. research assistant)
>
> - **small seminars** (<= 15 students)
> 
> - **large seminars** (>15 students)
>
> - listening to **presentations**
>
> - **reading clubs**
>
> - **study projects**
>
> - solving homework **exercises** in student groups
>
> - working on **group projects** (papers/presentations...)
>
> - working as a **HiWi**
>
> - participating in **extracurricular activities** (e.g. student body, university politics)
>
> - managing general **administration** tasks (e.g. examination office)


```{r, echo = F}
# read in the data
d <- read_csv('rand.csv')
d_lectures <- d %>% select(`Online classes work well for lectures (lecturer presents information)`: `Managing general administration tasks (e.g. examination office) remotely works fine.`)
# use more tractable col names
lecture_name <- c(
  "lectures",
  "tutorials",
  "Testate",
  "small seminars",
  "large seminars",
  "presentations",
  "reading clubs",
  "study projects",
  "exercises",
  "group projects",
  "HiWi",
  "extracurricular",
  "administration"
)
colnames(d_lectures) <- lecture_name
```


```{r, fig.height = 20}

d_lectures %>% 
  pivot_longer(cols = everything(), names_to = "question", values_to = "answer") %>% 
  mutate(
    question = factor(question, levels = lecture_name)
  ) %>% 
  filter(! is.na(answer)) %>% 
  ggplot(aes(x = answer)) +
  geom_bar() +
  facet_grid(question ~.) +
  scale_x_discrete(limits = 1:10) +
  labs(
    x = "rating",
    y = "frequency",
    title = "The online format works well for ... (1 = do not agree; 10 = agree)"
  )

```

## Free text answers

When asked whether they want to add something specific about the parts of online university that work well or not so well or if  they have suggestions on how to improve the shortcomings of specific types of sessions the students answered freely. The number in front of the quotes represent the participant number. The quotes are sorted
according to their topic. Within the blocks the first part are additions to the question “What works/What doesn’t?”, the latter part are suggestions to improve the shortcomings.
Hence, when a participant answered both, their number appears two times. Spelling was not corrected.
When sensible a rough Recap is added to summarise the results, sorted according to the number of students mentioned an issue/suggestion

### Lectures  

1: Some courses [...] don’t offer tutorial/practice session at all.  
2: the big blue button channel works great for lectures but not really for tutorials.  
3: Tutorials are not always given.  
4: Lectures are missing and the content isn’t well transmitted through online lectures. Currently I’m learning solely by books and the web. I would like to have at least some guidance from our lecturer on where to look for information or which content should be looked at more closely.  
5: It is annoying when video recordings etc. are uploaded unreliable (e.g. one week on monday and the other on thursday), that makes it hard to create oneself a fixed time schedule.  
6: Some classes are not well adapted to total virtual platforms. The classes are basically composed of a almost 2 hours video and 60-80 slides. That’s all. Given classes are online. then the strategy should be a different one. I would rather watch a 20 minutes video explaining straight away what is important and answer some questions in between. and then spend the rest of the time researching for answering some extra question the professor formulates than just passively listening him talk  
7: I don’t think online lectures work well as the uploaded videos often have a very bad quality or are even missing. In addition to that it is also harder to ask the lecturer questions, as they often don’t offer QA sessions.  
8: communication especially regarding the exams, also from WS19/20.  
9: The quality of the lecture strongly depends on the motivation of the lecturer to make the lecture work.  
10: More Live Streams would be appreciated.  
11: If online lectures work is dependent in the lecturer. It can be frustrating, when lectures do not upload their material in time since this can disrupt the study Plan that one has created quite a bit. The quality of the online presentation in most lectures exceeds expectations  
12: Whether online classes (lecturer presents information) work well depends completely on how it is done: Just doing a regular lecture and recording it is not really helpful, but they are exhausting. Doing those live, with us having to attend, is even worse. Really making use of the available digital means is awesome, though; e.g. short pod- and/or screencasts, a well balanced mix of online tutorials and reading assignments, even VIPS can be really great.  
13: I am positively suprised how well the Testate are going.  
14: Trying to improve the actual passive 2 hours video-slide format of the lectures would be a great start.  
15: Eventhough the online format suits the lectures, the quality of the resulting programs varies. E.g. it would be beneficial if lecturers adjusted their style for prerecorded lectures. Since we do not see each other in person, the (in my opinion silly) pressure to avoid just reading off of a script is non-existant. I’d much prefer you reading a script if it meant that the information was conveyed in
a more concise way. At least one lecturer appears to utilize editing techniques in their prerecorded videos, making cuts. Whether this is to just take a break, edit out mistakes, or to select a better take, I appreciate this. I can’t reasonably expect everybody to learn about video editing, but it can significantly improve the quality of the lectures.  
16: minimum 3 weeks before announcing a exam not just 8 days (Intro to Neuro, WS19/20)  
17: Online classes work perfectly for lectures if they are recorded. It happens that there are a lot of lags to people with bad connection, especially in lectures with lots of people. So being available to watch the lecture later is a must in my opinion  
18: One professor introduced question and answer sessions every 4th week or so which made it possible to ask questions about the lectures we have heard so far. I really liked this idea to balance out the missing interaction we normally have between students and professor (i.e. if the lecture is not held online).  
19: if the lecture isnt live online, I would really recommend theme-structured videos. Makes it easier to listen and structure your study.  
20: PLEASE DON’T try to just cram physical lectures/seminars into a digital format. As stated before, there are great ways to embrace digital formats - which of course have shortcomings of their own - but please understand that it’s a different beast than regular/classical formats and thus have to be implemented differently.  
21: Especially with lectures where a lot a videos are uploaded, I find that the time requirement to work through them is a lot higher than with normal lectures. I feel like when studying from home everything takes longer than it usually does and this is not really considered 144: For lectures: I appreciate the audio files put into the presentations, I would suggest to meet via BBB every two weeks to give room for questions regarding the content (like QQ but more often and periodic)  

#### Recap - Lectures  

Transfer lectures 1-to-1 as online material (e.g. talking while showing slides) alone does not support the student’s learning success (3 students)  
Offering additional Question and Answer Sessions helps the students to understand the material (3 students)    
Videos and material should always be uploaded at the same time to support the students in structuring their week (3 students)   
Having shorter videos (20 min) mixed with interactive parts (e.g questions, short independent research tasks, VIPs) would be preferred (2 students)  
Having live lectures is bad, bad internet connections (either because of number of attendees or technical issues at home) make recordings necessary (2 students)   
More live streams are appreciated (1 student)   
Tutorials are sometimes missing or not offered at all (2 students)  
Spoken text accompanying the slides can be scripted (if it improves content/structure), editing (making breaks, selecting the best take) is highly appreciated (1 student)  
Structuring the videos according to their theme helps students to listen to them and structure their studies accordingly (1 student)  
Videos are better than “real” sessions because one can pause and rewind to deepen the understanding (1 student)  
Following and understanding an online lecture takes longer than the mere video length (1 student)  
Giving some hints where students can find reliable extra material on specific topics is appreciated (1 student)  
Quality of the videos is bad (1 student)  
Quality of most lectures exceed expectations (1 student)  
Communication in regard to exams (also of last semester) should be improved and exams should
be announced at least 3 weeks in advance (1 student)  
Testate work well (1 student)  

### Seminars

1: [...] from my experience most students dont want to turn on their microphone, so no one is speaking except the tutor. people try to explain their question in the chats, which usually leads to misunderstandings.. It’s pretty exhausting.  
2: In Seminars the online format doesn’t really invite discussion that much especially because I for example don’t have a working mic or camera on my laptop so I can’t speak in discussions and will have to use my phone to record myself during presentations.  
3: I feel that when a seminar just consists of a student presentation each week (not even a discussion taking is taking place), I do not learn something. Especially when the lecturer neither provides additional content nor criticism on the presentation.  
4: Seminars are not really what they are supposed to be (at least the one I am taking at the moment) since it is mostly the professor or a student that is giving a presentation talking, but not really an active discussion between students and professor.  
5: In my opinion the most important part of a seminar is the open discussion between participants and lecturers. This is not really possible im the bbb-seminars that i have seen so far.  
6: [...] I participated in a small seminar and as soon as verbal exchange start in a Zoom-session, it starts to not work smoothly. People definitely interact more dynamically in a real world setting + technological issues (that still happen) make progressing at good speeds hard.  
7: make it obligatory to speak up? one probably cant do that.  
8: Sadly not. I find it hard to discuss in a chat as one can not see the faces of the interlocutor   
9: Personal discussions and interactions are really missing, and small group assignments might be nice to compensate this.  
10: Giving students feedback about their planned presentation beforehand and afterwards would be valuable.  
11: Everything with more than 30 students as an online live session (tutorials, seminars,..) get’s a little chaotic usually, maybe have more smaller seminars? or more tutors?  
12: [...] For Seminars: it would be nice to use the techniqual advantages even more - icluding videos, breakout rooms and other to higher the students engagement  
13: Create smaller seminars, splitting them into subgroups. Tutors should talk up more frequently and make sure no question is missed.  

#### Recap - Seminars

Discussions are exacerbated in online seminars (either because of the setting in general or technical
issues) (8 students).  
This is worsen in large seminars, hence, smaller groups are appreciated (2 students). Alternatively small group assignments could be nice to compensate this (1 student).   Or make it obligatory to speak up in an discussion (1 student).  
Using more of the technical possibilities (e.g. videos, breakout rooms, other means to engage the students) would be appreciated (1 student).  
Receiving feedback before and after a planned presentation would be valuable (1 student)  

### General Lectures/Seminars

1: It is incredibly hard to reach some professors, they just do not reply to emails or calls...  
2: Sometimes perhaps better prepare lecturers and tell them what (new) resources they can use.  
3: using the possibilities of the online tools, like little quizzes during a session to make it interactive for the students. [...]  
4: Teach the lecturers a more extensive use of Stud.IP for setting up Lectures/Schedules/Resoruces in an organised way (E.g Courseware). Its all there, it seems like most just don’t know.  
5: Please more interactive use of the courseware (as e.g. Tobias Thelen does);  
6: [...] So, what I want to say is that adding more work load to the course (in the middle of the semester) in times of online university is something that definitely does not work well.  
7: better prepare professors/lecturers for situations like these  

#### Recap - General Lectures/Seminars  

Prepare the teachers to make use of the resources to create interactive and organized material (e.g. Courseware, quizzes) (5 students).  
It is hard to reach some professors (1 student).    
Changing the workload during the semester is not appreciated as it deranges the planning (1 student)    

### BigBlueBottom and Stud.Ip

1: The stud.ip courseware (if used well) helps to follow the red thread of a course  
2: BBB has problems in one of my courses, in otheres it works fine  
3: BBB has sometimes problems but zoom always worked also for large groups. So would be nice if BBB could also improve the quality.  
4: Add a function to raise a hand in BBB  
5: We definitely need a better online teaching/learning platform than studIP. It has a lot of limitations that hamper the whole process of effectively providing and presenting study material to the students.  

#### Recap - BBB and Stud.Ip

BBB occasionally has issues to work reliably (2 students).  
Adding a function to raise a hand in BBB would be appreciated (1 student).  
If Stud.Ip courseware is used well, it helps the students to follow a course (1 student).  
There is a need for a better teaching/learning platform than Stud.Ip as it has many limitations (1 student).  

### Examination Office

1: The examination office is particularly slow to respond to emails and other requests like registration of thesis, etc.  
2: Nowadays it is very difficult to reach the examination office.  
3: The Pr¨fungsamt is doing a great job!  

####  Recap - Examination Office

The examination office is slow to respond or difficult to reach (2 students) and the examination office is doing a great job (1 student)  

### Technical Issues

1: The well working parts depend on a good internet connection;)  
2: In general online lectures should work really well because they are often not that interactive and could easily be recorded but unfortunately in my experience the recordings often lack quality.  
3: [...] Without access to university printers, printing becomes a tour de force.  
4: some professors/lecturers do not have the technical lnow-how to guarantee for example good audio quality  
5: Its difficult doing paper work, without having the possibility to use a printer. (As it is not allowed in the library)  
6: [...] And if every lecturer let’s us download the content since sometimes it’s not possible for me to watch them online because of my Internet connection.  
7: [...] better microphones for the lecturers (quality is often bad)  

#### Recap Technical Issues

The recordings have suboptimal audio quality (2 students).  
The students internet connection is hindering them to watch the (live) lectures (2 students).  
The missing access to printers is problematic (2 students).  

### Meta Critique

1: It is all very relativ.. The lectures work well compared to what? How it was before; then it is bad. How it works compared to other universities or schools: good enough. I think the problem is that this semester still counts as a normal semester (as far as I know), which is highly unfair. I would consider all of the classes much better if it would be a choice to take them.  
2: Yes, I love the fact that evaluations are getting more project-based and getting further away from tests. Tests suck! They are stressful and not that accurately representing ones’ understanding and learning of the topics. I’m so enjoying this online phase.  
3: In general Lecturers / anyone in teaching should be aware of how problematic the situation is and be careful to be *extremely* forgiving with regards to deadlines, examination strategies, etc. There many issues students have to tackle right now which might render them unable to actively take part in studying, which are not at all their fault - help these students to still be able to finish their courses.  

### Homework/Projects/Presentation/General Study Organization

1: Probably the biggest problem I have this semester is homework and projects. Working together just works so much better when you sit next to each other and can see what the other person is doing. Screensharing crowds your own screen, pointing at stuff simply does not work. Also I see no alternative for this. Just sucks.  
2: I really like online presentations since one does not have to stand in front of the whole class but rather can sit at home while giving the presentation. That might be more comfortable for shy persons.  
3: Regarding presentations it is much harder to concentrate if you don’t see the presenter and also as a presenter to give a good presentation without being able to read the audience. It can be hard to find study/presentation groups if you take part in a course without knowing anyone and not being able to talk to someone in person.  
4: [..]Another thing that does not work for me online are group presentations. [...]  
5: Organizationally it works really well, but it is really exhausting both on body and mind to have everything going on online.  
6: [...] For homework: be more dynamic and flexible for the amount of homework, instead of having one big performance goal, use a learning goal. Studying by myself makes it easier to learn without a heavy time pressure, but I need more time for solving homeworks and preparing the material from the lectures. It is quite uncomfortable to watch at a screen for more than 6 hours a day  

### Social Aspects

1: i cannot collaborate, discuss or group study with fellows. i cannot discuss my research ideas with a process if i happen to pass them by in the corridor or i see their office door open.  
2: Studying is a lot more fun and a lot more productive and creative if you have spontaneous and regular contact to other people. This is a fundamental part of research and studying that is missing totally in an online university.  

#### Recap - Social Aspects

Studying, discussing, generally research is missing a fundamental part when there is no regular contact with other people (2 students).


# 3. Problems encountered during the "digital" semester

```{r, echo = F}
# read in the data
d <- read_csv('rand.csv')
# get the relevant part
d_problems <- d %>% select(`How problematic was the summer term 2020 for you in general?`:`To cope with any arising issues, which of the following services have you used?`)
# use more tractable col names
colnames(d_problems) <- c(
  "how problematic",
  "which problems",
  "psychol. problem?",
  "psychol. problem worsened?",
  "personal report",
  "services used"
)
```

In this section we had wanted to specifically ask which (if any) problems arose for the students due to the Covid-19 crisis in general and the online semester in particular.

## How problematic was the summer term in gernal?

The question asked was:

> How problematic was the summer term 2020 for you in general?

Answers could be given on a 10-point Likert scale ranging from 1 (= very easy / no problems at all) to 10  (= very problematic / many problems). The distribution of answers is shown below.

```{r}
d_problems %>%
  # mutate(`how problematic` = as.character(`how problematic`)) +
  ggplot(aes(x = `how problematic`)) +
  geom_bar() +
  scale_x_discrete(limits = 1:10) +
  labs(
    x = "rating",
    y = "frequency",
    title = "How problematic was the SS 2020 in general (1 = easy; 10 = hard)?"
  )
```



## Which issues were encountered?

The question asked was:

> Which of the following issues or problems affected you as a result of the Covid-19 crisis and/or the online semester?

This question asked for (multiple selection) of pre-given issues which students may have faced. Here's the frequency with which each issue was selected. Note that only 14 participants indicated "no particular issue".

```{r}

fixed_items_q4.2 <- c("physical health issues", "mental health issues", "financial issues", "social issues", "term abroad cancelled / postponed", "internship (or similar) cancelled / postponed", "could not travel to Germany", "issues with technical equipment (computer, internet, ...)", "issues with access to study material (library, labs)", "no particular issues")

d_4.2 <- d_problems %>%
  separate(
    col = `which problems`,
    into = str_c(1:8),
    sep = ";",
    convert = T
  ) %>%
  select(2:9) %>%
  pivot_longer(
    cols = 1:8,
    names_to = "number",
    values_to = "item"
  ) %>%
  count(
    item
  ) %>%
  filter( ! is.na(item)) %>%
  arrange(-n)

d_q4.2_fixed <- d_4.2 %>% filter(item %in% fixed_items_q4.2)
d_q4.2_other <- d_4.2 %>% filter(! item %in% fixed_items_q4.2)

d_q4.2_fixed %>%
  # mutate(`how problematic` = as.character(`how problematic`)) +
  ggplot(aes(x = fct_reorder(`item`, n), y = `n`)) +
  geom_col() +
  coord_flip() +
  # scale_x_discrete(limits = 1:10) +
  labs(
    x = "",
    y = "frequency of selection",
    title = "Which issues did you encounter?"
  ) +
  theme(axis.text.y  = element_text(angle=15, vjust=0.5))
```

The question also allowed for specification of "other issues" unmentioned in our pre-given list. Here are the `r length(as.character(d_q4.2_other$item))` issues mentioned additionally:

```{r, results = 'asis'}
# map_chr(d_q4.2_other$item, function(i) i)

cat(paste('1.', as.character(d_q4.2_other$item) ), sep = '\n')
```

## Psychological problems

The question asked was:

> Do you suffer from any psychological conditions?


```{r}
d_q4.3 <- d_problems %>% select(`psychol. problem?`)
d_q4.3 %>%
  count(`psychol. problem?`) %>%
  filter(!is.na(`psychol. problem?`)) %>%
  ggplot(aes(x = fct_reorder(`psychol. problem?`, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "Psychological conditions?"
  )
```

A follow-up was asked as well, namely:

> If you suffer from any psychological conditions, did your situation worsen since March 2020?

```{r}
d_q4.4 <- d_problems %>% select(`psychol. problem worsened?`)
d_q4.4 %>%
  count(`psychol. problem worsened?`) %>%
  filter(!is.na(`psychol. problem worsened?`)) %>%
  ggplot(aes(x = fct_reorder(`psychol. problem worsened?`, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "Psychological conditions?"
  )
```

## Open question: other issues?

We also asked for any other issues to report freely:

> If you like, please tell us about any particularly striking problems that you encountered personally. If possible, please mention ways in which similar problems could be preventable or solvable for others in the future.

The answers given are listed here:

```{r, results = 'asis'}
d_q4.5 <- d_problems %>% select(`personal report`) %>%
  filter(! is.na(`personal report`)) %>%
  pull(`personal report`) %>%
  as.character()

cat(paste('1.', d_q4.5 ), sep = '\n')
```

## Which help was made use of?

We asked:

> To cope with any arising issues, which of the following services have you used?

Participants selected from a pre-defined list (multiple selections possible), but could also indicate 'other':

```{r}
fixed_items_q4.6 <- c("Advice mentoring team", "Advice Fachschaft", "Advice study coordinator", "Advice dean of studies", "Psychological counseling", "Examination office", "None")

d_4.6 <- d_problems %>%
  select(`services used`) %>%
  separate(
    col = `services used`,
    into = str_c(1:5),
    sep = ";",
    convert = T
  ) %>%
  pivot_longer(
    cols = everything(),
    names_to = "number",
    values_to = "item"
  ) %>%
  count(
    item
  ) %>%
  filter( ! is.na(item)) %>%
  arrange(-n)

d_q4.6_fixed <- d_4.6%>% filter(item %in% fixed_items_q4.6)
d_q4.6_other <- d_4.6 %>% filter(! item %in% fixed_items_q4.6)

d_q4.6_fixed %>%
  # mutate(`how problematic` = as.character(`how problematic`)) +
  ggplot(aes(x = fct_reorder(`item`, n), y = `n`)) +
  geom_col() +
  coord_flip() +
  # scale_x_discrete(limits = 1:10) +
  labs(
    x = "",
    y = "frequency of selection",
    title = "Which help did you use?"
  ) +
  theme(axis.text.y  = element_text(angle=15, vjust=0.5))

```

Here is are the answers given for the open question regarding which other services participants had relied on:

```{r, results = 'asis'}
cat(paste('1.', as.character(d_q4.6_other$item) ), sep = '\n')
```



# 4. Study Load/Progress

In this section we were trying to obtain information about how "efficient" the online semester appears to be.

```{r}
# get the relevant part
d_studyload <- d %>% select(`How many ECTS points are you aiming to get this semester?`:`If you have no yet completed all of your courses from the winter term, do you already know when and how you will be able to complete these courses?`)
# use more tractable col names
colnames(d_studyload) <- c(
  "ECTS points",
  "classes dropped",
  "how many courses?",
  "how much work?",
  "more semesters",
  "live sessions",
  "completed wi term?",
  "information about retakes"
)
```

## ECTS point goal for this semester

We asked:

> How many ECTS points are you aiming to get this semester?"

The question asked for pre-given amounts of ECTS points student are aiming to get ranging from "less than 15 ECTS" to "more than 30 ECTS". Here's the frequency with which each amount of ECTS points was selected.

```{r}
d_4.1 <- d_studyload %>%
  select(1) %>%
  pivot_longer(
    cols = 1,
    names_to = "label",
    values_to = "item"
  ) %>%
  count(
    item
  ) %>%
  # One person selected two answers, "25 ECTS" and "30 ECTS". I chose to not include these answers. NAs are filtered out as well.
  filter( ! is.na(item) & ! item == "25 ECTS;30 ECTS")

d_4.1 %>%
  mutate(item = fct_relevel(item, "less than 15 ECTS", "15 ECTS", "20 ECTS", "25 ECTS", "30 ECTS", "more than 30 ECTS")) %>%
  ggplot(aes(x = item, y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "How many ECTS points?"
  )
```


## Classes dropped

We asked:

> How many classes did you drop because of the current situation?

The question asked for pre-given amounts of dropped classes ranging from "1" to "4" and also "None" and "All". Here's the frequency with which each amount of dropped classes was selected.

```{r}
d_4.2 <- d_studyload %>%
  select(2) %>%
  pivot_longer(
    cols = 1,
    names_to = "label",
    values_to = "item"
  ) %>%
  count(
    item
  ) %>%
  filter( ! is.na(item)) %>%
  arrange(n)

d_4.2 %>%
  ggplot(aes(x = fct_reorder(`item`, n, .desc=TRUE), y = `n`)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "How many dropped classes?"
  )
```

## Change of course load

We asked:

> Are you currently following more or less courses than in other semesters?

Answers could be given on a 5-point scale ranging from "much less" to "much more". The distribution of answers is shown below.

```{r}
d_4.3 <- d_studyload %>%
  select(`how many courses?`) %>%
  pivot_longer(
    cols = 1,
    names_to = "label",
    values_to = "item"
  ) %>%
  count(
    item
  ) %>%
  filter( ! is.na(item))

d_4.3 %>%
  mutate(item = fct_relevel(item, "much less", "a bit less", "about the same", "a bit more", "much more")) %>%
  ggplot() +
  geom_col(aes(x = item, y = n)) +
  labs(
    x = "",
    y = "frequency",
    title = "Following how many courses compared to other semesters?"
  )
```

## General work load (compared to previous semesters)

We asked

> How much work are the current digital courses compared to usual university courses?

Answers could be given on a 10-point Likert scale ranging from "way less work" to "way more work". The distribution of answers is shown below.

```{r}
d_studyload %>%
  ggplot(aes(x = `how much work?`)) +
  geom_bar() +
  scale_x_discrete(limits = 1:10) +
  labs(
    x = "rating",
    y = "frequency",
    title = "How much work are digital courses compared to usual university courses (1 = way less work; 10 = way more work)?"
  )
```

## Study delay

We asked:

> Do you think that you will need more semesters than planned to complete your studies because of Corona?

The given answer options were "No", "Yes, one semester more" and "Yes, more than one semester more".

```{r}
d_4.5 <- d_studyload %>% select(`more semesters`)
d_4.5 %>%
  count(`more semesters`) %>%
  filter(!is.na(`more semesters`)) %>%
  ggplot(aes(x = fct_reorder(`more semesters`, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "Need more semester than planned due to Corona?"
  )
```

## Participation in live online lectures / seminars

We asked: 

> Are you regularly taking part in lectures or seminars that are broadcasted live?

Participants could choose between the two answers "Yes" and "No". The distribution of answers is shown below.

```{r}
d_4.6 <- d_studyload %>% select(`live sessions`)
d_4.6 %>%
  count(`live sessions`) %>%
  filter(!is.na(`live sessions`)) %>%
  ggplot(aes(x = fct_reorder(`live sessions`, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "Regularly attending live lectures or seminars?"
  )
```

## Winter term 19/20 completed?

We asked:

> Have you been able to complete all your courses from the winter term?

Participants could choose between the two answers "Yes" and "No". The distribution of answers is shown below.

```{r}
d_4.7 <- d_studyload %>% select(`completed wi term?`)
d_4.7 %>%
  count(`completed wi term?`) %>%
  filter(!is.na(`completed wi term?`)) %>%
  ggplot(aes(x = fct_reorder(`completed wi term?`, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "Been able to complete all courses from the winter term?"
  )
```

We also asked a follow-up:

> If you have no yet completed all of your courses from the winter term, do you already know when and how you will be able to complete these courses?

Participants could again choose between the two answers "Yes" and "No". The distribution of answers is shown below.

```{r}
d_4.8 <- d_studyload %>% select(`information about retakes`)
d_4.8 %>%
  count(`information about retakes`) %>%
  filter(!is.na(`information about retakes`)) %>%
  ggplot(aes(x = fct_reorder(`information about retakes`, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "If not: Do you already know when and how you will be able to complete these courses?"
  )
```

# 5. Social Life/Collaboration

In this section, we asked about how students organize their free time and collaboration with other students.

```{r}
# filepath = "C:/Users/Sarah/Documents/CogSci-SOS/data-raw.csv"
social = read_csv("rand.csv") %>% select(35:38)
```


## Online study group meetings

We asked:

> How often do you arrange meetings with other people for studying?

Responses were:

```{r}
social %>% 
  mutate(frequency = `How often do you arrange meetings with other people for studying?`) %>%   mutate(frequency = factor(frequency, levels = c('less often than in previous semesters', 'about the same', 'more often than in previous semesters'))) %>% 
  filter(!is.na(frequency)) %>% 
  ggplot(aes(frequency)) +
  geom_bar() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency",
    title = "Online study group meetings?"
  )

```

We also followed up:

> Do you meet virtually with people for studying?

Answers were:

```{r}
social %>% 
  mutate(meet = `Do you meet virtually with people for studying?`) %>% 
  filter(!is.na(meet)) %>% 
  ggplot()  +
  geom_bar(aes( `Do you meet virtually with people for studying?`)) +
  labs(
    x = "",
    y = "frequency",
    title = "Do you meet virtually with people for studying?"
  )
```

## Desire for online social activity

We asked:

> Would you wish there would be more online social events?

Answers were:

```{r}
social %>% 
  mutate(social = `Would you wish there would be offer more online social events?`) %>% 
  filter(! is.na(social)) %>% 
  ggplot()  +
  geom_bar(aes(social)) +
  labs(
    x = "",
    y = "frequency",
    title = "Would you wish there would be more online social events?"
  )
```




```{r}
# read in the data
d <- read_csv('rand.csv')
# get the relevant part
d_problems <- d %>% select(`How problematic was the summer term 2020 for you in general?`:`To cope with any arising issues, which of the following services have you used?`)
# use more tractable col names
colnames(d_problems) <- c(
  "how problematic",
  "which problems",
  "psychol. problem?",
  "psychol. problem worsened?",
  "personal report",
  "services used"
)
```


```{python, echo=F, eval=F}
# standard imports
import numpy as np
import pandas as pd
import matplotlib.pyplot as plt
import seaborn as sns
# sns.set_style("whitegrid")
# download the answer file from "Google Sheets" as a csv and save on your computer
# filepath = 'C:/Users/Sarah/Documents/CogSci-SOS/data-raw.csv' # change to your specific filepath (be aware of Windows/Linux/Apple conventions)
#filepath = "/home/god/Desktop/XY/uni/SS20/SOS/CogSciSOS.csv"
filepath = "data-raw.csv"
# Mood & Impressions
part1_1 = pd.read_csv(filepath, header=0, usecols = [1,2,3], names = ["Studies", "GeneralMood", "Expectations"]) #closed questions
part1_2 = pd.read_csv(filepath, header=0, usecols = [4]) # open questions
# Visualization of the first block of questions (closed ones)
mean1_1 = part1_1[["Studies", "GeneralMood", "Expectations"]].mean()
print("How is the the first online semester holding up in regards to your...\n",mean1_1.round(decimals =2))
# To plot general mood and impressions
fig1_1, ax1_1 = plt.subplots()
ax1_1.set_title('How is the the first online semester holding up in regards to your...')
part1_1[["Studies", "GeneralMood", "Expectations"]].boxplot(ax = ax1_1)
plt.xticks(ticks= [1,2,3],labels = ["Studies","General\nMood", "Expectations"],fontsize = "large")
plt.ylabel("Bad                                                     Well")
plt.show()
```

# 7. Final questions

```{r}
final <- read_csv('rand.csv') %>% select(53:57) %>% 
  mutate(
    program = `What program are you enrolled in?`,
    semester = `What semester are you in?`,
    know = `In case the next semester will be an online semester like the current, how important would it be for you to know this as soon as possible?`,
    remarks = `Please share anything that so far you had no chance of mentioning!`
  ) %>% select(program, semester, know, remarks)
```

## Who took this survey

We asked participants to give their study program and their semester.

```{r}
final %>%
  filter(! is.na(program)) %>% 
  ggplot(aes(program)) +
  geom_bar()
```

```{r}
final %>%
  filter(! is.na(semester)) %>% 
  ggplot(aes(semester)) +
  geom_bar()
```

## Certainty about winter term

We asked:

> In case the next semester will be an online semester like the current, how important would it be for you to know this as soon as possible?

Here is the distribution of answers:

```{r}
final %>% filter(!is.na(know)) %>% 
  mutate(know = factor(know, levels = c("It doesn't matter at all when I would know", "Good to know at some point but not urgent", "Very important to know ASAP"))) %>% 
  ggplot(aes(know)) + 
  geom_bar() +
  coord_flip()
```

## Final remarks

We also encouraged to give any final remarks:

> Please share anything that so far you had no chance of mentioning!

Here is what was written:

```{r, results = 'asis'}
remarks <- final %>% select(remarks) %>%
  filter(! is.na(`remarks`)) %>%
  pull(`remarks`) %>%
  as.character()

cat(paste('1.', remarks ), sep = '\n')
```

