---
title: "Report on Survey among Students of Cognitive Science / Computing"
output: 
  html_document:
    toc: true
    toc_depth: 2
    highlight: tango
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, echo = F)
```

```{r, echo = F}
library(tidyverse)
library(scales)
library(reticulate)
# use_condaenv('survey')
# setwd("C:\\Users\\Sarah\\Documents\\CogSci-SOS")
```

# 4. Questions about problems

```{r, echo = F}
# read in the data
d <- read_csv('data-raw.csv')
# get the relevant part
d_problems <- d %>% select(`How problematic was the summer term 2020 for you in general?`:`To cope with any arising issues, which of the following services have you used?`)
# use more tractable col names 
colnames(d_problems) <- c(
  "how problematic",
  "which problems",
  "psychol. problem?",
  "psychol. problem worsened?",
  "personal report",
  "services used"
)
```

INSERT TEXT: Motivation behind this question set (copy-paste in part from survey).

## Q4.1: "How problematic was the summer term 2020 for you in general?"

The question asked was "How problematic was the summer term 2020 for you in general?". Answers could be given on a 10-point Likert scale ranging from 1 (= very easy / no problems at all) to 10  (= very problematic / many problems). The distribution of answers is shown below. 

```{r}
d_problems %>% 
  # mutate(`how problematic` = as.character(`how problematic`)) +
  ggplot(aes(x = `how problematic`)) +
  geom_bar() +
  scale_x_discrete(limits = 1:10) +
  labs(
    x = "rating",
    y = "frequency",
    title = "How problematic was the SS 2020 in general (1 = easy; 10 = hard)?"
  )
```



## Q4.2: "Which of the following issues or problems affected you as a result of the Covid-19 crisis and/or the online semester?"

This question asked for (multiple selection) of pre-given issues which students may have faced. Here's the frequency with which each issue was selected. Note that only 14 participants indicated "no particular issue". 

```{r}

fixed_items_q4.2 <- c("physical health issues", "mental health issues", "financial issues", "social issues", "term abroad cancelled / postponed", "internship (or similar) cancelled / postponed", "could not travel to Germany", "issues with technical equipment (computer, internet, ...)", "issues with access to study material (library, labs)", "no particular issues")

d_4.2 <- d_problems %>% 
  separate(
    col = `which problems`,
    into = str_c(1:8),
    sep = ";",
    convert = T
  ) %>% 
  select(2:9) %>% 
  pivot_longer( 
    cols = 1:8, 
    names_to = "number", 
    values_to = "item"
  ) %>% 
  count(
    item
  ) %>% 
  filter( ! is.na(item)) %>% 
  arrange(-n)

d_q4.2_fixed <- d_4.2 %>% filter(item %in% fixed_items_q4.2)
d_q4.2_other <- d_4.2 %>% filter(! item %in% fixed_items_q4.2)

d_q4.2_fixed %>% 
  # mutate(`how problematic` = as.character(`how problematic`)) +
  ggplot(aes(x = fct_reorder(`item`, n), y = `n`)) +
  geom_col() +
  coord_flip() +
  # scale_x_discrete(limits = 1:10) +
  labs(
    x = "",
    y = "frequency of selection",
    title = "Which issues did you encounter?"
  ) +
  theme(axis.text.y  = element_text(angle=15, vjust=0.5))
```

The question also allowed for specification of "other issues" unmentioned in our pre-given list. Here are the `r length(as.character(d_q4.2_other$item))` issues mentioned additionally:

```{r, results = 'asis'}
# map_chr(d_q4.2_other$item, function(i) i)

cat(paste('1.', as.character(d_q4.2_other$item) ), sep = '\n')
```

## Q4.3 "Do you suffer from any psychological conditions?"

```{r}
d_q4.3 <- d_problems %>% select(`psychol. problem?`)
d_q4.3 %>% 
  count(`psychol. problem?`) %>% 
  filter(!is.na(`psychol. problem?`)) %>% 
  ggplot(aes(x = fct_reorder(`psychol. problem?`, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "Psychological conditions?"
  )
```

## Q4.4 "If you suffer from any psychological conditions, did your situation worsen since March 2020?"

```{r}
d_q4.4 <- d_problems %>% select(`psychol. problem worsened?`)
d_q4.4 %>% 
  count(`psychol. problem worsened?`) %>% 
  filter(!is.na(`psychol. problem worsened?`)) %>% 
  ggplot(aes(x = fct_reorder(`psychol. problem worsened?`, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "Psychological conditions?"
  )
```

## Q4.5 "If you like, please tell us about any particularly striking problems that you encountered personally. If possible, please mention ways in which similar problems could be preventable or solvable for others in the future."

```{r, results = 'asis'}
d_q4.5 <- d_problems %>% select(`personal report`) %>% 
  filter(! is.na(`personal report`)) %>% 
  pull(`personal report`) %>% 
  as.character()

cat(paste('1.', d_q4.5 ), sep = '\n')
```

## Q4.6 "To cope with any arising issues, which of the following services have you used?"

```{r}
fixed_items_q4.6 <- c("Advice mentoring team", "Advice Fachschaft", "Advice study coordinator", "Advice dean of studies", "Psychological counseling", "Examination office", "None")

d_4.6 <- d_problems %>% 
  select(`services used`) %>% 
  separate(
    col = `services used`,
    into = str_c(1:5),
    sep = ";",
    convert = T
  ) %>% 
  pivot_longer( 
    cols = everything(),
    names_to = "number", 
    values_to = "item"
  ) %>% 
  count(
    item
  ) %>% 
  filter( ! is.na(item)) %>% 
  arrange(-n)

d_q4.6_fixed <- d_4.6%>% filter(item %in% fixed_items_q4.6)
d_q4.6_other <- d_4.6 %>% filter(! item %in% fixed_items_q4.6)

d_q4.6_fixed %>% 
  # mutate(`how problematic` = as.character(`how problematic`)) +
  ggplot(aes(x = fct_reorder(`item`, n), y = `n`)) +
  geom_col() +
  coord_flip() +
  # scale_x_discrete(limits = 1:10) +
  labs(
    x = "",
    y = "frequency of selection",
    title = "Which help did you use?"
  ) +
  theme(axis.text.y  = element_text(angle=15, vjust=0.5))

```

Here is are the answers given for the open question regarding which other services participants had relied on:

```{r, results = 'asis'}
cat(paste('1.', as.character(d_q4.6_other$item) ), sep = '\n')
```



# 4. Study Load/Progress

In this section we were trying to obtain information about how "efficient" the online semester appears to be.

```{r}
# get the relevant part
d_studyload <- d %>% select(`How many ECTS points are you aiming to get this semester?`:`If you have no yet completed all of your courses from the winter term, do you already know when and how you will be able to complete these courses?`)
# use more tractable col names 
colnames(d_studyload) <- c(
  "ECTS points",
  "classes dropped",
  "how many courses?",
  "how much work?",
  "more semesters",
  "live sessions",
  "completed wi term?",
  "information about retakes"
)
```

## Q4.1: "How many ECTS points are you aiming to get this semester?"

The question asked for pre-given amounts of ECTS points student are aiming to get ranging from "less than 15 ECTS" to "more than 30 ECTS". Here's the frequency with which each amount of ECTS points was selected.

```{r}
d_4.1 <- d_studyload %>% 
  select(1) %>% 
  pivot_longer( 
    cols = 1, 
    names_to = "label", 
    values_to = "item"
  ) %>% 
  count(
    item
  ) %>% 
  # One person selected two answers, "25 ECTS" and "30 ECTS". I chose to not include these answers. NAs are filtered out as well.
  filter( ! is.na(item) & ! item == "25 ECTS;30 ECTS") 

d_4.1 %>% 
  mutate(item = fct_relevel(item, "less than 15 ECTS", "15 ECTS", "20 ECTS", "25 ECTS", "30 ECTS", "more than 30 ECTS")) %>% 
  ggplot(aes(x = item, y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "How many ECTS points?"
  ) 
```


## Q4.2: "How many classes did you drop because of the current situation?"

The question asked for pre-given amounts of dropped classes ranging from "1" to "4" and also "None" and "All". Here's the frequency with which each amount of dropped classes was selected.

```{r}
d_4.2 <- d_studyload %>% 
  select(2) %>% 
  pivot_longer( 
    cols = 1, 
    names_to = "label", 
    values_to = "item"
  ) %>% 
  count(
    item
  ) %>% 
  filter( ! is.na(item)) %>% 
  arrange(n) 

d_4.2 %>% 
  ggplot(aes(x = fct_reorder(`item`, n, .desc=TRUE), y = `n`)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "How many dropped classes?"
  ) 
```

## Q4.3: "Are you currently following more or less courses than in other semesters?"

The question asked was "Are you currently following more or less courses than in other semesters?". Answers could be given on a 5-point scale ranging from "much less" to "much more". The distribution of answers is shown below. 

```{r}
d_4.3 <- d_studyload %>% 
  select(`how many courses?`) %>% 
  pivot_longer( 
    cols = 1, 
    names_to = "label", 
    values_to = "item"
  ) %>% 
  count(
    item
  ) %>% 
  filter( ! is.na(item)) 
  
d_4.3 %>% 
  mutate(item = fct_relevel(item, "much less", "a bit less", "about the same", "a bit more", "much more")) %>% 
  ggplot() + 
  geom_col(aes(x = item, y = n)) + 
  labs(
    x = "",
    y = "frequency",
    title = "Following how many courses compared to other semesters?"
  )
```

## Q4.4: "How much work are the current digital courses compared to usual university courses?"

The question asked was "How much work are the current digital courses compared to usual university courses?". Answers could be given on a 10-point Likert scale ranging from "way less work" to "way more work". The distribution of answers is shown below. 

```{r}
d_studyload %>% 
  ggplot(aes(x = `how much work?`)) +
  geom_bar() +
  scale_x_discrete(limits = 1:10) +
  labs(
    x = "rating",
    y = "frequency",
    title = "How much work are digital courses compared to usual university courses (1 = way less work; 10 = way more work)?"
  )
```

## Q4.5: "Do you think that you will need more semesters than planned to complete your studies because of Corona?"

The question asked was "Do you think that you will need more semesters than planned to complete your studies because of Corona?". The given answer options were "No", "Yes, one semester more" and "Yes, more than one semester more".

```{r}
d_4.5 <- d_studyload %>% select(`more semesters`)
d_4.5 %>% 
  count(`more semesters`) %>% 
  filter(!is.na(`more semesters`)) %>% 
  ggplot(aes(x = fct_reorder(`more semesters`, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "Need more semester than planned due to Corona?"
  )
```

## Q4.6: "Are you regularly taking part in lectures or seminars that are broadcasted live?"

The question asked was "Are you regularly taking part in lectures or seminars that are broadcasted live?". Participants could choose between the two answers "Yes" and "No". The distribution of answers is shown below.

```{r}
d_4.6 <- d_studyload %>% select(`live sessions`)
d_4.6 %>% 
  count(`live sessions`) %>% 
  filter(!is.na(`live sessions`)) %>% 
  ggplot(aes(x = fct_reorder(`live sessions`, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "Regularly attending live lectures or seminars?"
  )
```

## Q4.7: "Have you been able to complete all your courses from the winter term?"

The question asked was "Have you been able to complete all your courses from the winter term?". Participants could choose between the two answers "Yes" and "No". The distribution of answers is shown below.

```{r}
d_4.7 <- d_studyload %>% select(`completed wi term?`)
d_4.7 %>% 
  count(`completed wi term?`) %>% 
  filter(!is.na(`completed wi term?`)) %>% 
  ggplot(aes(x = fct_reorder(`completed wi term?`, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "Been able to complete all courses from the winter term?"
  )
```

## Q4.8: "If you have no yet completed all of your courses from the winter term, do you already know when and how you will be able to complete these courses?"

The question asked was "If you have no yet completed all of your courses from the winter term, do you already know when and how you will be able to complete these courses?". Participants could again choose between the two answers "Yes" and "No". The distribution of answers is shown below.

```{r}
d_4.8 <- d_studyload %>% select(`information about retakes`)
d_4.8 %>% 
  count(`information about retakes`) %>% 
  filter(!is.na(`information about retakes`)) %>% 
  ggplot(aes(x = fct_reorder(`information about retakes`, n), y = n)) +
  geom_col() +
  coord_flip() +
  labs(
    x = "",
    y = "frequency of selection",
    title = "If not: Do you already know when and how you will be able to complete these courses?"
  )
```

# 5. Social Life/Collaboration

In this section, we are asking about how you organize your collaboration with other students. We also ask questions about your personal life. (All optional, of course!)

```{r}
# filepath = "C:/Users/Sarah/Documents/CogSci-SOS/data-raw.csv"
social = read_csv("data-raw.csv") %>% select(35:37)
```


## Q5.1 "How often do you arrange meetings with other people for studying?"

```{r}
ggplot(social)  + 
  geom_bar(aes( stringr::str_wrap(`How often do you arrange meetings with other people for studying?`, 20))) + 
  labs(
    x = "",
    y = "frequency",
    title = "How often do you arrange meetings with other people for studying?"
  )

```

## Q5.2 "Do you meet virtually with people for studying?"
```{r}


ggplot(social)  + 
  geom_bar(aes( stringr::str_wrap(`Do you meet virtually with people for studying?`, 20))) + 
  labs(
    x = "",
    y = "frequency",
    title = "Do you meet virtually with people for studying?"
  )

```

## Q5.3 "Would you wish there would be offer more online social events?"

```{r}

ggplot(social)  +
  geom_bar(aes( stringr::str_wrap(`Would you wish there would be offer more online social events?`, 20))) +
  labs(
    x = "",
    y = "frequency",
    title = "Would you wish there would be offer more online social events?"
  )
```




```{r}
# read in the data
d <- read_csv('data-raw.csv')
# get the relevant part
d_problems <- d %>% select(`How problematic was the summer term 2020 for you in general?`:`To cope with any arising issues, which of the following services have you used?`)
# use more tractable col names 
colnames(d_problems) <- c(
  "how problematic",
  "which problems",
  "psychol. problem?",
  "psychol. problem worsened?",
  "personal report",
  "services used"
)
```


# Testing out python integration

```{python, echo=F}
# standard imports 
import numpy as np
import pandas as pd 
import matplotlib.pyplot as plt
import seaborn as sns
# sns.set_style("whitegrid")
# download the answer file from "Google Sheets" as a csv and save on your computer
# filepath = 'C:/Users/Sarah/Documents/CogSci-SOS/data-raw.csv' # change to your specific filepath (be aware of Windows/Linux/Apple conventions)
#filepath = "/home/god/Desktop/XY/uni/SS20/SOS/CogSciSOS.csv"
filepath = "data-raw.csv"
# Mood & Impressions
part1_1 = pd.read_csv(filepath, header=0, usecols = [1,2,3], names = ["Studies", "GeneralMood", "Expectations"]) #closed questions
part1_2 = pd.read_csv(filepath, header=0, usecols = [4]) # open questions
# Visualization of the first block of questions (closed ones)
mean1_1 = part1_1[["Studies", "GeneralMood", "Expectations"]].mean()
print("How is the the first online semester holding up in regards to your...\n",mean1_1.round(decimals =2))
# To plot general mood and impressions 
fig1_1, ax1_1 = plt.subplots()
ax1_1.set_title('How is the the first online semester holding up in regards to your...')
part1_1[["Studies", "GeneralMood", "Expectations"]].boxplot(ax = ax1_1)
plt.xticks(ticks= [1,2,3],labels = ["Studies","General\nMood", "Expectations"],fontsize = "large")
plt.ylabel("Bad                                                     Well")
plt.show()
```
