---
title: "Report on Survey among Students of Cognitive Science / Computing"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = F, message = F, echo = F)
```

```{r, echo = F}

library(tidyverse)
library(scales)
library(reticulate)

```


```



# Section 5 Social Life/Collaboration

In this section, we are asking about how you organize your collaboration with other students. We also ask questions about your personal life. (All optional, of course!)

```{r}
filepath = "/home/god/Desktop/XY/uni/SS20/SOS/CogSciSOS.csv"
social = read_csv(filepath) %>% select(35:37)
```


## Q5.1 "How often do you arrange meetings with other people for studying?"

```{r}
ggplot(social)  + 
  geom_bar(aes( stringr::str_wrap(`How often do you arrange meetings with other people for studying?`, 20))) + 
  labs(
    x = "",
    y = "frequency",
    title = "How often do you arrange meetings with other people for studying?"
  )

```

## Q5.2 "Do you meet virtually with people for studying?"
```{r}


ggplot(social)  + 
  geom_bar(aes( stringr::str_wrap(`Do you meet virtually with people for studying?`, 20))) + 
  labs(
    x = "",
    y = "frequency",
    title = "Do you meet virtually with people for studying?"
  )

```

## Q5.3 "Would you wish there would be offer more online social events?"

```{r}

ggplot(social)  +
  geom_bar(aes( stringr::str_wrap(`Would you wish there would be offer more online social events?`, 20))) +
  labs(
    x = "",
    y = "frequency",
    title = "Would you wish there would be offer more online social events?"
  )
```




```{r}
# read in the data
d <- read_csv('data-raw.csv')
# get the relevant part
d_problems <- d %>% select(`How problematic was the summer term 2020 for you in general?`:`To cope with any arising issues, which of the following services have you used?`)
# use more tractable col names 
colnames(d_problems) <- c(
  "how problematic",
  "which problems",
  "psychol. problem?",
  "psychol. problem worsened?",
  "personal report",
  "services used"
)
```

# Questions about problems

INSERT TEXT: Motivation behind this question set (copy-paste in part from survey).

## Q4.1: "How problematic was the summer term 2020 for you in general?"

The question asked was "How problematic was the summer term 2020 for you in general?". Answers could be given on a 10-point Likert scale ranging from 1 (= very easy / no problems at all) to 10  (= very problematic / many problems). The distribution of answers is shown below. 

```{r}
d_problems %>% 
  # mutate(`how problematic` = as.character(`how problematic`)) +
  ggplot(aes(x = `how problematic`)) +
  geom_bar() +
  scale_x_discrete(limits = 1:10) +
  labs(
    x = "rating",
    y = "frequency",
    title = "How problematic was the SS 2020 in general (1 = easy; 10 = hard)?"
  )
```




